### 2020-07-20 code/figure1.Rmd
change coordinate object to have  a column explicitly called sample_id and not row.names

cluster_umap <- uwot::umap(mca_res$ind$coord,
  min_dist = 1e-6,
  n_components = 3,
  n_neighbors = round(sqrt(nrow(mca_res$ind$coord))),
  n_epochs = 1000,
  n_threads = 1
)
colnames(cluster_umap) <- c("cluster_x", "cluster_y", "cluster_z")
hdb_cluster_assignment <- hdbscan(cluster_umap, minPts = optimal_minPts)
umap_3d_coors <- gdc_umap_coors %>%
  bind_cols(as.data.frame(cluster_umap)) %>%
  mutate(
    clust = as.factor(hdb_cluster_assignment$cluster),
    member_prob = hdb_cluster_assignment$membership_prob,
    row.names = rownames(gdc_umap_coors)
  )
## clust 0 is unclassified cluster

>>>>

cluster_umap <- uwot::umap(mca_res$ind$coord,
  min_dist = 1e-6,
  n_components = 3,
  n_neighbors = round(sqrt(nrow(mca_res$ind$coord))),
  n_epochs = 1000,
  n_threads = 1
)
colnames(cluster_umap) <- c("cluster_x", "cluster_y", "cluster_z")
hdb_cluster_assignment <- hdbscan(cluster_umap, minPts = optimal_minPts)
umap_3d_coors <- gdc_umap_coors %>%
  bind_cols(as.data.frame(cluster_umap)) %>%
  mutate(
    clust = as.factor(hdb_cluster_assignment$cluster),
    member_prob = hdb_cluster_assignment$membership_prob,
    sample_id = rownames(gdc_umap_coors)
  )
## clust 0 is unclassified cluster
